### 2008-12-20 talk/ecoop2009/clibackend.tex
fix another XXX
some minore changes

From the implementation point of view, the JIT generator is divided into a
frontend and several backends.  The goal of the frontend is to generate a JIT
compiler which works as described in the previous sections.  Internally, the
frontend represents the compiled code as \emph{flow graphs}, and the role of
the backends is to translate flowgraphs into machine code.

@@

Thus, when using the CLI backend, we actually have two layers of
JIT-compilation, each layer removing away different kinds of overhead.  By
operating at a higher level, our JIT can potentially do a better job than the
.NET one in some contexts, as our benchmarks demonstrate (see
section~\ref{sec:benchmarks}).  On the other hand, the lower-level .NET JIT is
very good at producing machine code, much more than PyPy's own \emph{x86}
backend for example.  By combining the strengths of both we can get highly
efficient machine code.

@@

\subsection{Implementing flexswitches in CLI}

>>>>

From the implementation point of view, the JIT generator is divided into a
frontend and several backends.  The goal of the frontend is to generate a JIT
compiler which works as described in the previous sections.  Internally, the
JIT represents the compiled code as \emph{flow graphs}, and the role of
the backends is to translate flowgraphs into machine code.

@@

Thus, when using the CLI backend, we actually have two layers of
JIT-compilation, each layer removing away different kinds of overhead.  By
operating at a higher level, our JIT can potentially do a better job than the
.NET one in some contexts, as our benchmarks demonstrate (see
Section~\ref{sec:benchmarks}).  On the other hand, the lower-level .NET JIT is
very good at producing machine code, much more than PyPy's own \emph{x86}
backend for example.  By combining the strengths of both we can get highly
efficient machine code.

@@

\subsection{Implementing flexswitches in CLI}
\label{sec:flexswitches-cli}

### 2008-12-20 talk/ecoop2009/tlc.tex
comment out a possible confusing example, and add an XXX
some minore changes

Obviously, not all the operations are applicable to all types. For example,
it is not possible to \lstinline{ADD} an integer and an object, or reading an
attribute from an object which does not provide it.  Being dynamically typed,
the VM needs to do all these checks at runtime; in case one of the check
fails, the execution is simply aborted.

@@

\subsection{TLC examples}

As we said above, TLC exists only at bytecode level; to ease the development
of TLC programs, we wrote an assembler that generates TLC bytecode. Figure \ref{fig:tlc-abs}
shows a simple program that computes the absolute value of
the given integer.

@@

@@

\begin{lstlisting}
def main(n):
    if n<0:
        return -n
    return n
\end{lstlisting}

>>>>

Obviously, not all the operations are applicable to all types. For example,
it is not possible to \lstinline{ADD} an integer and an object, or reading an
attribute from an object which does not provide it.  Being dynamically typed,
the interpreter needs to do all these checks at runtime; in case one of the check
fails, the execution is simply aborted.

@@

\subsection{TLC example}

As we said above, TLC exists only at bytecode level; to ease the development
of TLC programs, we wrote an assembler that generates TLC bytecode. Figure \ref{fig:tlc-abs}
shows a simple program that computes the absolute value of
the given integer.  In the subsequent sections, we will examine step-by-step 
how the generated JIT compiler manages to produce a fully optimized version of it.

@@

\commentout{

\anto{I think this example could cause confusion, because the synatx is TOO
  similar to (R)Python, hence in the next section it could be unclear which is
  the leves of the examples}

@@

\begin{lstlisting}
def main(n):
    if n<0:
        return -n
    return n
\end{lstlisting}
}
